---
title: "ODD Sales / March 2017"
author: "oktayekici"
date: "28 Oct 2018"
output: html_document
---

```{r message = FALSE}
library(dplyr)
library(tidyverse)
library(scales)
```


### Gathering the Data

Car sales report of March 2017 is downloaded from **ODD** website and renamed to "odd_retail_sales_2017_03.xlsx". And then the file is uploaded to github.

### Downloading the Raw Data:
This code is for creating a temporary .xlsx file, downloading raw data from local/github and refine for analysis:

```{r}
tmp<-tempfile(fileext=".xlsx")
download.file("https://github.com/MEF-BDA503/pj18-oktayekici/blob/master/odd_retail_sales_2017_03.xlsx?raw=true",destfile=tmp, mode = "wb")
raw_data<-readxl::read_excel(tmp,skip=7,col_names=FALSE)
file.remove(tmp)
raw_data <- raw_data %>% slice(-c(46,47))
head(raw_data)

```

## Editing Column Names

We are now editing column names for better look:

```{r}
#Adding column names
colnames(raw_data) <- c("brand_name","auto_dom","auto_imp","auto_total","comm_dom","comm_imp","comm_total","total_dom","total_imp","total_total")
#Changing nulls with "0"
car_data_mar_17 <- raw_data %>% mutate_if(is.numeric,funs(ifelse(is.na(.),0,.)))%>% mutate(year=2017,month=3)
print(car_data_mar_17,width=Inf)
```

## Saving Data
```{r}
saveRDS(car_data_mar_17,file="~/rodevi/odd_car_sales_data_mar_17.rds")
```
## First analysis
```{r}
car_data_mar_17 %>% 
    filter(auto_total > 0 & comm_total > 0) %>%
    select(brand_name,total_total) %>%
    arrange(desc(total_total))
```

Top domestic car productions by brand
```{r}
car_data_mar_17 %>% 
    filter(auto_total > 0 & comm_total > 0) %>%
    select(brand_name,total_dom) %>%
    arrange(desc(total_dom))
```